{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
added fullstop in figure
added explicit space in definition of next

\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] \in \text{SeqIns} \\ se, i \vdash_{seq} \textsc{s} \Rightarrow \textsc{t}}
{se, i \vdash \textsc{s} \Rightarrow \textsc{t}}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] = \mathtt{start}\ pc \\ se(i) \leq se(pc)}
{se, i \vdash \textsc{s} \Rightarrow \textsc{s}}
\end{align*}
\end{minipage}
\caption{Extension of the sequential typing rules}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

\begin{definition}{next}
For every branching point $c$ in the source program such that $\vdash_\circ [c]_\bullet^n$, we  have
that $\forall k \in tregion(n) . next(k) = jun(n)$.
\end{definition}

>>>>

\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] \in \text{SeqIns} \\ se, i \vdash_{seq} \textsc{s} \Rightarrow \textsc{t}}
{se, i \vdash \textsc{s} \Rightarrow \textsc{t}}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule{P[i] = \mathtt{start}\ pc \\ se(i) \leq se(pc)}
{se, i \vdash \textsc{s} \Rightarrow \textsc{s}}
\end{align*}
\end{minipage}
\caption{Extension of the sequential typing rules.}
\label{fig:multithreaded-typing-rules}
\end{figure}

@@

\begin{definition}{next}
For every branching point $c$ in the source program such that $\vdash_\circ [c]_\bullet^n$, we  have
that $\forall k \in tregion(n) .\ next(k) = jun(n)$.
\end{definition}
